?????????????????

### 2022-11-22 article_1/Conclusion.tex
Export the images directly to the LaTeX images folder

\noindent{The test using a simply synthetic sample shows the great capability of the method by retrieving not only the precisely center positions \ref{AppendixA.1} }

>>>>

\noindent{The test using a simply synthetic sample shows the great capability of the method by retrieving not only the precisely center positions }
